Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
5:30 push

Performance of parallel algorithms are usually measured in terms of 3 different metrics: speedup, strong scalling efficiency and weak scaling efficiency.

@@

Strong scaling 
Programs that are difficult to parallelize will have efficiency expressions like $\frac{1}{\ln p}$ which approaches zero as the number of processors increases by a large amount.

@@

>>>>

Performance of parallel algorithms are usually measured in terms of 3 different metrics: speedup, strong scalling efficiency and weak scaling efficiency.  Strong and weak scaling are common measures for the different ways a program can benefit from increased parallellism and more processors as well as the limitatios that dictate the speedups.

@@

Strong scaling is a way to measure performance of a given application depending on if it is CPU-bound. This means that 
Programs that are difficult to parallelize will have efficiency expressions like $\frac{1}{\ln p}$ which approaches zero as the number of processors increases by a large amount.

@@

\subsection{Amdahl's Law}

The final principle when discussing parallel performance is the potential existence of an Amdahl speedup limit.  o7777777777
